---
title: "Homework 9"
author: "Nithila Sathiya, EID: ns37382"
date: "2024-04-13"
output: pdf_document
---

```{r setup, echo = FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(mosaic)
library(ggplot2)
library(knitr)
library(kableExtra)
library(MatchIt)
library(moderndive)
```
Link to Github:

# Problem 1

## Part A
```{r echo = FALSE, message = FALSE, warning = FALSE}
gotv <- read.csv("turnout.csv")
prop(voted1998 ~ GOTV_call, data = gotv)

diff_voted = do(10000) * diffprop(voted1998 ~ GOTV_call, data = resample(gotv))
conf_voted <- confint(diff_voted, level = 0.95)
print(conf_voted)
```
The proportion of those who received a GOTV call and who voted in 1998 was 0.65. The proportion of those who did not receive a GOTV call and who voted in 1998 was 0.44. By conducting a large-sample 95% confidence interval for the difference in two proportions it was demonstrated that the difference is .20 about 95% of the time and fluctuates between .14-.26.

## Part B
```{r echo = FALSE, message = FALSE, warning = FALSE}
ggplot(gotv, aes(x = GOTV_call)) + geom_bar(aes(fill = factor(GOTV_call))) + facet_wrap(~voted1996) + xlab("voted1996")

ggplot(gotv, aes(x = AGE)) + geom_boxplot(aes(fill = factor(GOTV_call)))

ggplot(gotv, aes(x = GOTV_call)) + geom_bar(aes(fill = factor(GOTV_call))) + facet_wrap(~MAJORPTY) + xlab("MAJORPTY")
```
Based on the distribution of each variable based on whether or not they received a call, we can claim that the variables are confounders. This means that the true difference in proportions cannot be calculated based on only GOTV_call and voted1998.

## Part C
```{r echo = FALSE, message = FALSE, warning = FALSE}
gotv_match = matchit(GOTV_call ~ factor(voted1996) + AGE + factor(MAJORPTY), data = gotv, ratio = 5)

gotv_match_data = match.data(gotv_match)

prop(voted1998 ~ GOTV_call, data = gotv_match_data)
diff_match = do(10000) * diffprop(voted1998 ~ GOTV_call, data = resample(gotv_match_data))
conf_match <- confint(diff_match, level = 0.95)
print(conf_match)
```
The proportion of those who received a GOTV call is .65. The proportion of those who did not receive a GOTV call is .57. The difference in the two proportions fell 95% of the time between .008 and .138, with an estimate of .074.
```{r echo = FALSE, message = FALSE, warning = FALSE}
group1 <- gotv_match_data$voted1998[gotv_match_data$GOTV_call == 1]
group2 <- gotv_match_data$voted1998[gotv_match_data$GOTV_call == 0]

t_test_gotv <- t.test(group1, group2, var.equal = FALSE)
print(t_test_gotv)
```
I conducted a t-test to demonstrate the significance of the difference in proportion we found. Since the p-value is less than .05, we can conclude the the difference is statistically significant and that people are more likely to vote if they receive a GOTV call. This statement can be made because the difference is signficant and because the proportion of voter turnout for GOTV calls is higher than no GOTV calls.

# Problem 2

## Part A
```{r echo = FALSE, message = FALSE, warning = FALSE}
solder <- read.csv("solder.csv")
ggplot(solder, aes(x = skips, y = Opening)) + geom_boxplot() + xlab("Number of Skips") + ggtitle("Skips vs Opening Size")
```
The plot above demonstrates the relationship between the opening skips and the number of solder skips. The plot shows a higher median number of skips for the small size opening than the other sizes.

```{r echo = FALSE, message = FALSE, warning = FALSE}
ggplot(solder, aes(x = skips, y = Solder)) + geom_boxplot() + xlab("Number of Skips") + ggtitle("Skips vs Solder Thickness")
```
The plot above demonstrates the relationship between the soldering thickness and the number of skips. The plot shows a higher median number of skips for the thin solder than the thick solder.

## Part B
```{r echo = FALSE, message = FALSE, warning = FALSE}
lm_solder = lm(skips ~ Opening + Solder + Opening:Solder, data = solder)
get_regression_table(lm_solder, conf.level = 0.95, digits = 2)
```

## Part C
The table demonstrates that the coefficient for Opening:S is 5.13, meaning that if the opening compared to a different size opening (such as large), the number of skips increases by 5.13, the same logic applies to Opening:M whose coefficient is 2.41.
For the soldering thickness, the thin solder increases the number of skips by 2.28 in comparison to the thick solder.
When considering both variables the size small opening and the thin solder has an estimate of 9.65, suggesting that the number of skips increases by 9.65 in comparison to the other variables.

## Part D
I would suggest for AT&T to increase their opening size to large and make the solder thick. The table shows that as the opening size decreases, the number of skips increase. Since the small and thin combination results in the most number of skips, the opposite approach would decrease the number of skips the most you can.